% resume.tex
% vim:set ft=tex spell:
%project management in practice
\documentclass[10pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.35in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{hyperref}
%\usepackage{tgpagella}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
    {\setlength{\leftmargin}{#1}}%
    \item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
    {\setlength{\leftmargin}{-0.5#1}}%
    \item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\vspace{-0.05in}\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
    #1 &
    #2 \\
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

% and the actual content starts here
\begin{document}

\begin{center}
{\LARGE \textbf{\href{http://www.linkedin.com/in/liyi1989}{Yi Li}}}


260 Safford st.\ \ Quincy, MA, USA, 02170\\
(929) 231-7845\ \ \textbullet \ \ liyi.1989@gmail.com

\end{center}
\vspace{-0.25em}
\hrule \vspace{-0.75em}
\subsection*{Education}

\begin{itemize}
    \parskip=0.1em
    \item[]
    \headerrow
        {\textbf{Northeastern University (2013-Expected May 2017)}}
        {\textbf{Boston, MA}}
    \\
    \headerrow
        {\emph{PhD in Statistics, Mathematics}}
        {\emph{GPA: 4.00/4.00}}
    \begin{itemize*}
    	\item Preprint: Copula Correlation:  An Equitable Dependence Measure and Extension of Pearson’s Correlation.
        \item Relevant courses: Mathematical Statistics, Machine/Statistical Learning, Partial Differential Equations, etc.
    \end{itemize*}
    \item[]
    \headerrow
        {\textbf{Northeastern University (2011-2013)}}
        {\textbf{Boston, MA}}
    \\
    \headerrow
        {\emph{Master's of Science in Operations Research, Mathematics}}
        {\emph{GPA: 4.00/4.00}}
    \begin{itemize*}
        \item Relevant courses: Time Series Analysis, Applied Statistics, Operations Research, Financial Management.
    \end{itemize*}

\item[]
    \headerrow
        {\textbf{Yale University (Summer 2010)}}
        {\textbf{New Haven, CT}}
    \\
    \headerrow
        {\emph{Summer Session}}
        {\emph{GPA: 4.00/4.00}}
    \begin{itemize*}
        \item Relevant course: Computational Finance (derivatives pricing and GARCH models)
    \end{itemize*}

\item[]
    \headerrow
        {\textbf{Fudan University (2007-2011)}}
        {\textbf{Shanghai, China}}
    \\
    \headerrow
        {\emph{Bachelor's of Science in Information and Computational Science, Mathematics}}
        {\emph{GPA: 3.37/4.00}}
    \begin{itemize*}
        \item Relevant courses: Mathematical
        Finance, Numerical Analysis, Mathematical Modeling, System Modeling, Optimal Control Theory, Differential Equations, Probability, Mathematical Analysis, C++ Programming etc.
    \end{itemize*}


\end{itemize}

%=========================
\hrule
\vspace{-0.75em}
\subsection*{Experience}

\begin{itemize}
    \parskip=0.1em
    
    \item[]
    \headerrow
        {\textbf{Quanto.ml}}
        {\textbf{Boston, MA}}
    \\
    \headerrow
        {\emph{Quantitative Analyst Intern}}
        {\emph{Jun. 2015 -- Aug. 2015}}
    \begin{itemize*}
        \item Manipulating fundamental (panel) data for the listed companies with the Quantopian Research Platform(IPython Notebook based) with {\em pandas} and {\em seaborn}. Building machine learning algorithm for predicting the relative return.  
    \end{itemize*}
    
    \item[]
    \headerrow
        {\textbf{LLX solutions}}
        {\textbf{Waltham, MA}}
    \\
    \headerrow
        {\emph{Biostatistician Intern}}
        {\emph{Jun. 2015 -- Aug. 2015}}
    \begin{itemize*}
        \item Creating statistical analysis plans (SAP) based on protocols for drug development in phase II-IV.   
    \end{itemize*}
    
    \item[]
    \headerrow
        {\textbf{DataRobot}}
        {\textbf{Boston, MA}}
    \\
    \headerrow
        {\emph{Data Science Intern}}
        {\emph{Jun. 2014 -- Aug. 2014}}
    \begin{itemize*}
        \item Building repository for data manipulation, predictive models, visualization and reproducible research techniques with R(RStudio) and Python(IPython Notebook). Topics include GAM, PCA, LDA, PLS, MDS, SVM, KDE, clustering, R Markdown, Shiny, HDF5 files, etc.
    \end{itemize*}
    
    
    \item[]
    \headerrow
        {\textbf{Northeastern University}}
        {\textbf{Boston, MA}}
    \\
    \headerrow
        {\emph{Teaching Assistant/Math Tutor}}
        {\emph{Sep. 2011 -- Apr. 2014}}
    \begin{itemize*}
        \item Diff eq \& Lin Alg, Numerical Analysis, Statistics for bioinformatics(creating Coursera-style online course).
    \end{itemize*}
    
    \item[]
    \headerrow
        {\textbf{Bolton Works}}
        {\textbf{East Hartford, CT}}
    \\
    \headerrow
        {\emph{Math Advisor}}
        {\emph{Dec. 2012 -- Jan. 2013}}
    \begin{itemize*}
        \item Dealing with the transformation matrix related to the 3D scanning equipments via MATLAB and VBScript.
    \end{itemize*}
    

    \item[]
    \headerrow
        {\textbf{eXalt Solutions}}
        {\textbf{Cambridge, MA}}
    \\
    \headerrow
        {\emph{Data Management Specialist}}
        {\emph{Oct. 2012 -- Nov. 2012}}
    \begin{itemize*}
        \item QA the user reports and SKU reports for different clients on daily bases with Excel.
    \end{itemize*}





\item[]
    \headerrow
        {\textbf{Meritco Services (Consulting Company)}}
        {\textbf{Shanghai, China}}
    \\
    \headerrow
        {\emph{Due Diligence Intern}}
        {\emph{Aug. 2010}}
    \begin{itemize*}
        \item  Performed data entry and processing with Excel.
    \end{itemize*}



\end{itemize}
%=========================
\hrule \vspace{-0.75em}
\subsection*{Academic Projects}
\begin{itemize}
    \parskip=0.1em
\item[]
    \headerrow
        {\textbf{Forecasting conditional volatility with GARCH model}}{graduate course project}
    \vspace{-0.2in}
    \begin{itemize*}
        \item Modeled conditional volatility of the financial data with GARCH family models with Matlab and R
    \end{itemize*}
\item[]
    \headerrow
        {\textbf{Revenue Management for the air cargo arrangement}}{graduate course project}
    \vspace{-0.2in}
    \begin{itemize*}
        \item Modeled the single-leg air cargo revenue management by using the Markov Chain
    \end{itemize*}

\item[]
    \headerrow
        {\textbf{Optimal harvesting policy in marine reserves}}{\it{undergraduate thesis}}
    \vspace{-0.2in}
    \begin{itemize*}
        \item Utilized the optimal control theory to simulate and find the optimal harvesting policy by using Matlab
    \end{itemize*}


\end{itemize}
%==========================================================
\hrule \vspace{-0.75em}
\subsection*{Skills/Standard Exams}
\begin{itemize}
    \parskip=0.1em

\item[]
    \begin{itemize*}
        \item R, MATLAB, Python, C++, SAS, git, LINGO, \LaTeX, MS-Offce
        \item passed the Society of Actuaries(SOA) Exam P
        \item RankII(C++) of the National(China) Computer Rank
    Examination
       \item National(China) High School Mathematical Olympiad first place
       \item Fluent in Chinese and English
    \end{itemize*}



\end{itemize}
\end{document}
